ML parameters

### 2022-11-21 workflow/notebooks/ml-params.Rmd
updated plot axis labels

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, dataset, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

@@

results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, method, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

@@

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, metric, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

>>>>

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, dataset, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(y="dataset optimized during model training", x="performance on held out test data")
```

@@

results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, method, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(y="method optimized during model training", x="performance on held out test data")
```

@@

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, metric, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(y="metric optimized during model training", x="performance on held out test data")
```
